CYO Project Report - Delivery Prediction System

### 2021-07-21 finalReportPrep.Rmd
updated code with file references

```{r trained knn model based on train_subset, echo=FALSE }
load('rda/knn_model.rda')
knn_fit

knn_fit %>% ggplot()
```

Based on model results, k value of `r knn_fit$finalModel$k` was identified to be the one with lowest RMSE.

@@

Details of the trained random forest model can be found below:
```{r trained random forest model based on train_subset, echo=FALSE}
load('rda/rf_model.rda')
rf_fit

rf_fit %>% ggplot()
```

@@

Based on model results, mtry value of `r rf_fit$finalModel$mtry` was identified to be the one with lowest RMSE.

@@

```{r Tuning parameters to use for final random forest, echo=FALSE}
load('rda/rf_model.rda')

data.frame(tuning_parameter='mtry', value=rf_fit$finalModel$mtry) %>% add_row(tuning_parameter='number_of_trees', value=500) %>% knitr::kable(caption='Random forest tuning parameters')
```

@@

```{r trained final random forest model based on training_dataset, echo=FALSE}
load('rda/final_model.rda')
#final_model

plot(final_model,main='Random forest model error against number of trees')
```

@@

```{r Final knn model traing with data scaled, include=FALSE, eval= FALSE}
set.seed(seed=1,sample.kind = 'Rounding')
preProcessScalingValues <- preProcess(training_dataset %>% select(-number_of_hours), method = c("center", "scale"))

scaled_train_subset <- predict(preProcessScalingValues, training_dataset) 
scaled_test_subset <- predict(preProcessScalingValues, validation_dataset)

final_knn_fit <- knnreg(number_of_hours~., scaled_train_subset,k = knn_fit$finalModel$k)

final_knn_fit

predictions <- predict(final_knn_fit,scaled_test_subset %>% select(-number_of_hours))

RMSE(predictions,(scaled_test_subset %>% pull(number_of_hours) ))
# 202.8552

save(final_knn_fit,file='rda/final_knn_fit.rda')
```

```{r Final ensemble model, include=FALSE, eval= FALSE}
load('rda/final_knn_fit.rda')
load('rda/final_model.rda')

set.seed(seed=1,sample.kind = 'Rounding')

predictions_knn <- predict(final_knn_fit,scaled_test_subset %>% select(-number_of_hours))
predictions_rf <- predict(final_model,validation_dataset %>% select(-number_of_hours))

RMSE(rowMeans(predictions_df),(validation_dataset %>% pull(number_of_hours) ))
# 193.3459
```

>>>>

```{r trained knn model based on train_subset, echo=FALSE }
if(file.exists('rda/knn_model.rda')) { 
  load('rda/knn_model.rda'); 
  print(knn_fit);
} else {
  lines <- readLines('captured-outputs/knn_model_output.txt')
  cat(lines,sep="\n")

  rm(lines)
}
```

```{r print plot for knn model based on train_subset, echo=FALSE, out.width ="100%", fig.align='center'}
if(file.exists('rda/knn_model.rda')) { 
    knn_fit %>% ggplot() 
} else {
  knitr::include_graphics('captured-outputs/knn_model_plot.png')
}
```

Based on model results, k value of `r if(exists("knn_fit",mode="list")) { knn_fit$finalModel$k } else {77}` was identified to be the one with lowest RMSE.

@@

Details of the trained random forest model can be found below:
```{r trained random forest model based on train_subset, echo=FALSE}
if(file.exists('rda/rf_model.rda')) { 
  load('rda/rf_model.rda'); 
  print(rf_fit);
} else {
  lines <- readLines('captured-outputs/rf_model_output.txt')
  cat(lines,sep="\n")

  rm(lines)
}
```

```{r print plot for rf model based on train_subset, echo=FALSE, out.width ="100%", fig.align='center'}
if(file.exists('rda/rf_model.rda')) { 
    rf_fit %>% ggplot() 
} else {
  knitr::include_graphics('captured-outputs/rf_model_plot.png')
}
```

@@

Based on model results, mtry value of `r if(exists("rf_fit",mode="list")) { rf_fit$finalModel$mtry } else {2}` was identified to be the one with lowest RMSE.

@@

```{r Tuning parameters to use for final random forest, echo=FALSE}
mtry_value <- 2
if(file.exists('rda/rf_model.rda')) { 
  load('rda/rf_model.rda');
  mtry_value = rf_fit$finalModel$mtry
}

data.frame(tuning_parameter='mtry', value=mtry_value) %>% add_row(tuning_parameter='number_of_trees', value=500) %>% knitr::kable(caption='Random forest tuning parameters')

rm(mtry_value)
```

@@

Details of the final trained random forest model can be found below:

```{r trained final random forest model based on training_dataset, echo=FALSE}
if(file.exists('rda/final_model.rda')) {
  load('rda/final_model.rda')
  sink('captured-outputs/final_model_output.txt')
  print(final_model)
  sink()
}

lines <- readLines('captured-outputs/final_model_output.txt')
cat(lines,sep="\n")

if(exists("final_model",mode="list")) {
  plot(final_model,main='Random forest model error against number of trees')
} else {
  plot_object <- readRDS('rds/final_model_plot.rds')
  plot(plot_object,type='l',main='Random forest model error against number of trees', xlab='trees', ylab='Error')

  rm(plot_object)
}
```

@@
